---
title: "Statistik Stadt Zuerich Colors (zuericolors)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

zuericolors is an R-Package, which provides specific colors of the corporate design of the city of Zurich. The package contains all colors that [Statistik Stadt Zürich](https://www.stadt-zuerich.ch/prd/de/index/statistik.html) needs for the creation of graphics. There are two main functions in zuericolors:

* `get_zuericolors` extracts colors of a specific color palette and puts them into a vector.
* `view_zuericolors` prints a specific color palette and is useful for visual inspection.

## Installation
The easiest way to get zuericolors is to install it from this repo:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("StatistikStadtZuerich/zuericolors")
```

Alternatively, download the files (by clicking 'Clone or download' / 'Download Zip'), extract it to any location on your computer, e.g. to your Desktop:

```{r, eval = FALSE}
remotes::install_local("<path_to_location>/zuericolors-main", dependencies = FALSE)
```

## Version
To check your version of zuericolors, run:

```{r, eval = FALSE}
packageVersion("zuericolors")
```

## Usage

```{r, message = FALSE}
library(zuericolors)

# Get all the colors from palette "hamronic 6"
get_zuericolors("harmonic6")

# Get first color from palette "diverging5rotgruen"
get_zuericolors("diverging5rotgruen", nth = 1)

# Get first four colors from palette "contrasting12"
get_zuericolors("contrasting12", nth = 1:4)
```

